### 2020-09-12 code/figure4.Rmd

```{r forest-heatmap-data-plot, fig.align='center', fig.width= 9, fig.height= 8, message=FALSE}
#fig.width= 16, fig.height= 20,
load("../data/forest.heatmap.data.rda")

@@

all_compare_plot <- bind_rows(down_compare_plot, up_compare_plot)
all_compare_plot %<>% arrange(or, .by_group = TRUE) %>% mutate(Hugo_Symbol = as.character(Hugo_Symbol)) %>% ungroup() %>% mutate(Row_Index = sprintf("%3i", row_number()))
Hugo_rownames <- all_compare_plot$Hugo_Symbol
names(Hugo_rownames) <- as.character(all_compare_plot$Row_Index)
all_p <- ggplot(all_compare_plot, 
               aes(x = or,
                   y = Row_Index,
                   color = cluster,
                   group = cluster)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_pointrange(aes(xmin = ci.low, xmax = ci.up)) +
  scale_y_discrete(labels = Hugo_rownames) +
  scale_color_manual(values = cluster_colors) +
  theme_classic() +
  xlab("log odds ratio") +
  ylab("Gene") +
  facet_grid(cluster ~ ., scales = "free_y", drop = TRUE, space = "free_y", switch = "y") +
  theme(
    panel.grid.major.y = element_line(colour = "#f0f0f0"),
    axis.title.y = element_blank()
  )

tdat_all <- all_muts %>%
  filter(Hugo_Symbol %in% all_compare_plot$Hugo_Symbol) %>%
  distinct(Tumor_Sample_Barcode, Hugo_Symbol, clust_knn_char, type) %>%
  select(type, clust_knn_char, Hugo_Symbol) %>%
  table()
tdat_all <- left_join(
  as.data.frame(tdat_all),
  clinical_plus_cluster %>%
    select(Tumor_Sample_Barcode, type, clust_knn_char) %>%
    distinct() %>%
    group_by(type, clust_knn_char) %>%
    summarise(ntumors = n())) %>%
  group_by(type, clust_knn_char) %>%
  mutate(c_prop = Freq / ntumors) %>%
  mutate(c_prop = ifelse(is.na(c_prop), 0, c_prop)) %>%
  select(type, clust_knn_char, Hugo_Symbol, c_prop) %>%
  rename(cluster = clust_knn_char)
tdat_all <- all_compare_plot %>% left_join(tdat_all)
tdat_all_p <- tdat_all %>% ggplot(aes(type, Row_Index, fill = c_prop)) +
  geom_tile() +
  scale_fill_viridis_c(option = "E", "Proportion of \nTumor Type \nMutated Within Cluster", limits = c(0, 1)) +
  xlab("Tumor Type") +
  ylab("Gene Symbol") +
  scale_y_discrete(labels = Hugo_rownames) +
  facet_grid(cluster ~ ., scales = "free_y", drop = TRUE, space = "free_y") +
  theme_classic() +
  theme(
    strip.text = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major.y = element_line(colour = "#f0f0f0")
  )

>>>>

```{r forest-heatmap-data-plot, fig.align='center', fig.width= 8, fig.height= 10.25, message=FALSE}
load("../data/forest.heatmap.data.rda")

@@

all_compare_plot <- bind_rows(down_compare_plot, up_compare_plot)
all_compare_plot %<>% arrange(or, .by_group = TRUE) %>% mutate(Hugo_Symbol = as.character(Hugo_Symbol)) %>% ungroup() %>% mutate(Row_Index = sprintf("%3i", row_number()))
Hugo_rownames <- all_compare_plot$Hugo_Symbol
names(Hugo_rownames) <- as.character(all_compare_plot$Row_Index)
all_p <- ggplot(all_compare_plot, 
               aes(x = or,
                   y = Row_Index,
                   color = cluster,
                   group = cluster)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_pointrange(aes(xmin = ci.low, xmax = ci.up, fatten = 1)) +
  scale_y_discrete(labels = Hugo_rownames) +
  scale_color_manual(values = cluster_colors) +
  theme_classic() +
  xlab("log odds ratio") +
  ylab("Gene") +
  facet_grid(cluster ~ ., scales = "free_y", drop = TRUE, space = "free_y", switch = "y") +
  theme(
    panel.grid.major.y = element_line(colour = "#f0f0f0"),
    axis.text.y = element_text(size = 8),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8)
  )

tdat_all <- all_muts %>%
  filter(Hugo_Symbol %in% all_compare_plot$Hugo_Symbol) %>%
  distinct(Tumor_Sample_Barcode, Hugo_Symbol, clust_knn_char, type) %>%
  select(type, clust_knn_char, Hugo_Symbol) %>%
  table()
tdat_all <- left_join(
  as.data.frame(tdat_all),
  clinical_plus_cluster %>%
    select(Tumor_Sample_Barcode, type, clust_knn_char) %>%
    distinct() %>%
    group_by(type, clust_knn_char) %>%
    summarise(ntumors = n())) %>%
  group_by(type, clust_knn_char) %>%
  mutate(c_prop = Freq / ntumors) %>%
  mutate(c_prop = ifelse(is.na(c_prop), 0, c_prop)) %>%
  select(type, clust_knn_char, Hugo_Symbol, c_prop) %>%
  rename(cluster = clust_knn_char)
tdat_all <- all_compare_plot %>% left_join(tdat_all)
tdat_all_p <- tdat_all %>% ggplot(aes(type, Row_Index, fill = c_prop)) +
  geom_tile() +
  scale_fill_viridis_c(option = "E", "Proportion of \nTumor Type \nMutated Within Cluster", limits = c(0, 1)) +
  xlab("Tumor Type") +
  ylab("Gene Symbol") +
  scale_y_discrete(labels = Hugo_rownames) +
  facet_grid(cluster ~ ., scales = "free_y", drop = TRUE, space = "free_y") +
  theme_classic() +
  theme(
    strip.text = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 8),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8),
    panel.grid.major.y = element_line(colour = "#f0f0f0")
  )
